---
title: "Windance Demo Gear"
author: "Jason Elder"
date: "2025-01-21"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

1.  How to check items in and out of the demo fleet.
2.  How to add items to the demo fleet
3.  How to delete items from the demo fleet.

## Checking items in and out of the Demo fleet (IPads)

-   Go to Librarika App
-   select Passwords
-   select the Librarika Password
-   Ask Customer if they have used the Demo fleet this year
-   if they have not, create a New `Member` Account

### 1. Creating a New Member Account

-   Select Members at the bottom of the screen
-   Select `+` at the top Right of the screen
-   Complete these Fields: 
- `Member No.` = `Customer Phone Number`
- `Phone Number` 
- `Name`
- `Email`
- `Phone`

-   Select Save
-   Navgate to the Home Page

### 2. Have Cusotmer Fill out Liability Waiver

- Blank pages are stored under the desk. 

### 3. Check-Out

-   ALL items must be checked in and out. Each individual item. Seriously tho...

-   Press the `Quick Check Out` button

-   Enter `Customer Phone Number` in the `Member No.` Field

-   Scan item using the Ipad Camera

-   Select the correct item that pops up

-   Select `Do Again` to add more items

-   Select `Done` when all items are added

### 4. Payment in Lightspeed

- Collect Payment in Lightspeed


### 5. Check-In

-   Select `Quick Check-In`

-   Check Item For damage

-   Scan Item

-   Add Remark for any damage noticed. Otherwise type `No Damage` and your initials.

## 6. Permanently Adding and Deleting Items From the demo fleet.

When a product is sold/lost/stolen/Moved to Consignment complete this form to remove it from the Demo Fleet Inventory System (Librarika).

```{r QRcode, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.width=3, fig.height=3, fig.align='center'}
library(tinytex)
library(qrcode)

plot(qr_code('https://docs.google.com/forms/d/e/1FAIpQLSddpF90TXOApElrylcqBXn94vBJvAAdQsdwZ03dcEXqjBl4Lw/viewform'))

```

When a New Item is added to the Demo Fleet. Complete this form to have it added to the Demo Fleet Inventory Managment System (Librarika).

```{r QRcode2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.width=3, fig.height=3, fig.align='center'}

plot(qr_code('https://docs.google.com/forms/d/e/1FAIpQLSddpF90TXOApElrylcqBXn94vBJvAAdQsdwZ03dcEXqjBl4Lw/viewform'))

```

## 7. Updating The Demo Fleet Booklet and Printing New Demo Fleet stickers.

Ask Jason or Nick

The script for genreating new Barcodes is in the Windance GitHub Account Repository `LibrarikaBarcodes`.

See The ReadMe file in GitHub for Steps.

### 8. Questions

-   For addional questions ask ChatGPT, if that doesnt cut it ask Jason.
