---
title: "Windance Demo Gear"
author: "Jason Elder"
date: "2025-01-21"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

1.  How to check items in and out of the demo fleet.
2.  How to add items to the demo fleet
3.  How to delete items from the demo fleet.

## Checking items in and out of the Demo fleet (IPads) 
- Go to Librarika App
- select Passwords
- select the Librarika Password
- Ask Customer if they have used the Demo fleet this year
- if they have not, create a New `Member` Account

### Creating a New Member Account

- Select Members at the bottom of the screen
- Select `+` at the top Right of the screen
- Complete these Fields:
-- Member No. = Customer Phone Number
-- Name
-- Email
-- Phone
- Select Save
- Navgate to the Home Page

### Check-Out
- ALL items must be checked in and out. Each individual item. Seriously tho... 

-   Press the ` Quick Check Out` button
-   Enter `Customer Phone Number` in the `Member No.` Field
-   Scan item using the Ipad Camera
-  Select the correct item that pops up
- Select `Do Again` to add more items
- Select `Done` when all items are added

### Check-In

-   Select `Quick Check-In`

-   Check Item For damage

-   Scan Item

-   Add Remark for any damage noticed. Otherwise type `No Damage` and your initials.


## Permanently Adding and Deleting Items From the demo fleet.

When a product is sold/lost/stolen/Moved to Consignment complete this form to remove it from the Demo Fleet Inventory System (Librarika).

```{r QRcode, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(tinytex)
library(qrcode)

plot(qr_code('https://docs.google.com/forms/d/e/1FAIpQLSddpF90TXOApElrylcqBXn94vBJvAAdQsdwZ03dcEXqjBl4Lw/viewform'))

```

When a New Item is added to the Demo Fleet. Complete this form to have it added to the Demo Fleet Inventory Managment System (Librarika).

```{r QRcode, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

plot(qr_code('https://docs.google.com/forms/d/e/1FAIpQLSddpF90TXOApElrylcqBXn94vBJvAAdQsdwZ03dcEXqjBl4Lw/viewform'))

```

## Updating The Demo Fleet Booklet and Printing New Demo Fleet stickers.

Ask Jason or Nick

The script for genreating new Barcodes is in the Windance GitHub Account Repository `LibrarikaBarcodes`.

See The ReadMe file in GitHub for Steps.

### Questions

- For addional questions ask ChatGPT, if that doesnt cut it ask Jason. 
