---
title: "Windance Demo Gear"
author: "Jason Elder"
date: "2025-01-21"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

1.  How to check items in and out of the demo fleet.
2.  How to add items to the demo fleet.

## Checking items in and out of the Demo fleet (IPads)

-   Go to Demo Gear on the Home Screen
-   select Passwords
-   select the Librarika Password
-   Ask Customer if they have used the Demo fleet this year
-   if they have not, create a New `Member` Account

### 1. Creating a New Member Account

-   Select Members at the bottom of the screen

-   Select `+` at the top Right of the screen

-   Complete these Fields:

-   `Member No.` = `Customer Phone Number`

-   `Phone Number`

-   `Name`

-   `Email`

-   Select Save

-   Navgate to the Dashboard (Top of the Side bar on the Left)

### 2. Have Cusotmer Fill out Liability Waiver

-   Blank pages are stored under the desk.

### 3. Check-Out

-   All Items should have a Barcode on them with the exception of Leashes, Hardware, and Handles

-   Press the `Check Out` button on the Dashboard

-   Enter `Customer Name` and Select From the Drop down

-   enter product SKU or Scan With camera

-   Select the correct item from the drop down Menu

-   Select `Submit`

-   to add More Items simply repeat. All selected Items with appear in Grey.

-   Select `Done` when all items are added.

### 4. Payment in Lightspeed

-   Collect Payment in Lightspeed

### 5. Check-In

-   Select `Check-In`

-   Check Item For damage

-   Scan Item or enter the SKU in the System

-   Add Remark for any damage noticed. Otherwise type `No Damage` and your initials.

## 6. Permanently Adding and Deleting Items From the demo fleet.

When a product is sold/lost/stolen/Moved to Consignment complete this form to remove it from the Demo Fleet Inventory System (Librarika).

```{r QRcode, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.width=3, fig.height=3, fig.align='center'}
library(tinytex)
library(qrcode)

plot(qr_code('https://docs.google.com/forms/d/e/1FAIpQLSddpF90TXOApElrylcqBXn94vBJvAAdQsdwZ03dcEXqjBl4Lw/viewform'))

```

When a New Item is added to the Demo Fleet. Complete this form to have it added to the Demo Fleet Inventory Managment System (Librarika).

```{r QRcode2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.width=3, fig.height=3, fig.align='center'}

plot(qr_code('https://docs.google.com/forms/d/e/1FAIpQLSddpF90TXOApElrylcqBXn94vBJvAAdQsdwZ03dcEXqjBl4Lw/viewform'))

```

## 7. Printing New Demo Fleet stickers.

1.  Navigate to Github and Login using TeamPassword
2.  Navigate to the **LibrarikaBarcodes** Repository.
3.  Open the Data folder. There should be 1 file in this folder.
4.  Open Librarika in a new tab
5.  Navigate to Reports \> Catelogue Reports \> Export all Copies and download
6.  Upload this file to the Data folder in Github
7.  Delete the old file from github. DO NOT DELETE BEFORE ADDING THE NEW FILE AS IT WILL DELETE THE FOLDER AS WELL
8.  Go to Actions
9.  Select Generate Barcode PDFs on the Left of the page.
10. Select Run Workflow
11. The code takes about 5 minutes to run
12. Navigate to LibrarikaLabels.pdf and Download the FIle.
13. Open this new file. It has all the labels for the Demo Fleet.
14. Select The Label you want to Print and Print it using the waterproofs labels in the Zebra printer
15. Done

Notes: this will NOT work if you **Export all Titles** from Librarika.....
